The Received Signal Code Power (RSCP) measured on the Primary CPICH. The reference point for the RSCP shall be the antenna connector of the UE. The reporting range for CPICH RSCP is from $-124$ dBm to $-25$ dBm [TS 25.215].

The \textit{Ec/N0} is identical to RSCP/RSSI. Measurement shall be performed on the Primary CPICH. The reporting range of it is from $-24$ dBm to $0$ dB [TS 25.215].

%\IfFileExists{./legend/Scans-Plot-Serving--3G--SigPow.tex}{%
%\vfill
%\begin{table}[H]
%\centering
%\begin{subtable}[b]{0.48\textwidth}\centering\large
%\input{./legend/Scans-Plot-Serving--3G--SigPow}
%\end{subtable}
%\begin{subtable}[b]{0.48\textwidth}\centering\large
%\input{./legend/Scans-Plot-Serving--3G--SigQual}
%\end{subtable}
%\end{table}
%\vfill
%}{}


\AddPicLegOutG{Scans-Plot-Serving--3G--SigPow}{Received Signal Code Power (\textit{RSCP}) for 3G Serving Cell.}
\AddPicLegOutG{Scans-Plot-Serving--3G--SigQual}{Signal Quality (\textit{Ec/N0}) for 3G Serving Cell.}
\AddPicLegOutG{Scans-Plot-Neighbor--3G--SigPow}{Received Signal Code Power (\textit{RSCP}) for 3G Neighbor Cell.}
\AddPicLegOutG{Scans-Plot-Neighbor--3G--SigQual}{Signal Quality (\textit{Ec/N0}) for 3G Neighbor Cell.}
\AddPicLegOutG{Scans-Plot-Serving,Neighbor--3G--SigPow}{Received Signal Code Power (\textit{RSCP}) for 3G Serving and Neighbor Cell.}
\AddPicLegOutG{Scans-Plot-Serving,Neighbor--3G--SigQual}{Signal Quality (\textit{Ec/N0}) for 3G Serving and Neighbor Cell.}

\clearpage
\AddTableOMultiPage{Scans-Table-Serving--3G-}{Scan results for Serving cell in 3G}
\clearpage
\AddTableOMultiPage{Scans-Table-Neighbor--3G-}{Scan results for Neighbor cell in 3G}
\clearpage
\AddTableOMultiPage{Scans-Table-Serving,Neighbor--3G-}{Scan results for  Serving and Neighbor cell in 3G}
